Analyzing the impact of social attributes on the success of commit integration

### 2017-02-17 Paper/MSRChallenge2017.tex
removed result line

\begin{abstract}
Abstract goes here
\end{abstract}

@@

The dataset provided by the MSR Challenge~\cite{msr17challenge} is very diverse 
and consists of commits that date from very far back, and the social data we are 
gathering is recent data, gathered in January 2017. The researchers of this 
project acknowledge this discrepancy and in an effort to mitigate this threat to 
validity, we filter the commits analyzed by looking only at the commits pushed 
in the last 3 years of the dataset (2014,2015,2016), with the intuition that the 
social data gathered by this study will have a closer relationship to the social 
data if it were to be gathered in these years, than if we would compare it to 
years further back.

\todo{Explain downsampling}

@@

\section{Results}
Results \todo{maybe this section can be merged with the prior one} Table \ref{resultsTable}

@@

\section{Discussion}
Discussion

@@

\noindent\textbf{External validity:} 
External validity threats deal with the generalizability of our findings. 
To tackle the concern that the results of this study might not generalize to other studies outside of the studied cases, we have used a broad and rich dataset~\cite{msr17challenge} in our analysis.

\noindent\textbf{Construct validity:}
Regarding the suitability of our evaluation metrics,

\section{Conclusion}
The conclusion goes here. this is more of the conclusion

>>>>

\begin{abstract}
\todo{Abstract goes here}
\end{abstract}

@@

The dataset used in this study~\cite{msr17challenge} is very diverse 
and consists of commits that date from far back, and the social data we are 
gathering is recent data, gathered in January 2017. The researchers of this 
project acknowledge this discrepancy and in an effort to mitigate this threat to 
validity, we filter the commits analyzed by looking only at the commits pushed 
in the last 3 years of the dataset (2014,2015,2016), with the intuition that the 
social data gathered by this study will have a closer relationship to the social 
data if it were to be gathered in these years, than if we would compare it to 
years further back.

We constructed a decision tree with the dataset before mentioned, and we noticed that at this point the training data was unbalanced in a ratio close to 3:1 regarding successful and unsuccessful instances accordingly. To mitigate the risk of this being a skewing factor for the training process of the decision tree, we sampled randomly the successful instances to get an equal distribution of 
successful and unsuccessful instances to train the decision tree. We present the results of both of these datasets in the following section.

@@

\section{Results}

@@

\section{Discussion}
In this study we have analyzed how considering social data is beneficial to be able to predict if a commit will be successfully integrated into a project or not. We have analyzed different technical complexity measures that work as a proxy for the complexity of the task being commited, such as number of files added, size of the project, size of the commit, etc. It is worth noticing that these are not the only measures that can be used as a proxy for technical complexity of a commit. The same intuition applies to the social attributes we gathered. These are not the only proxies for experience a developer may have, but we are making use of a suitable feature Github provides, which are the social attributes being measured in this study.

This study is consistent with previous studies~\cite{Yu15,tsay14icse,tsay14fse} that show the importance of considering social traits  when dealing with a merely social process such as the software development process.

@@

\noindent\textbf{External validity:} 
External validity threats deal with the generalizability of our findings. 
To tackle the concern that the results of this study might not generalize to 
other instances outside of the studied cases, we have used a broad and rich 
dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
projects used in this dataset have also been filtered to be popular (having more 
than 10 watches on Github), and to have a history of using the continuous 
integration tool Travis CI for more than 50 builds. All these features help to 
build the notion that since we are building our analysis on top of a vast 
dataset comprehending a wide diversity of projects, the threat of this analysis 
not generalizing to other projects is mitigated.

\noindent\textbf{Construct validity:}
Regarding the suitability of our evaluation metrics, the authors understand that 
Travis job success is not the only way to analyze the success of a commit, and 
that for different reasons the job may not be successful even if the code 
commited does not have flaws (a flacky test case for example). Since continuous 
integration is a best known practice in industry and the use of this methodology 
spreads out into the open source community, we consider that cases of misuse of 
CI such that it will lead to failing travis jobs when they should have actually 
be successful are minimum, specially since having a solid build is one of the 
main purposes of the methodology, and taking into account that the projects in 
out dataset are projects with a history of using continuous integration and 
having a certain level of popularity, this threat is minimized. We therefore 
consider Travis job success to be a proxy 
for success when integrating a commit into a larger project.

\section{Conclusion}
In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
Afterwards, we have gathered social attributes from the developers who pushed each of these commits
and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
instances.

Our results show that adding social data to the construction of the decision tree increases the probability this correctly predicting future commit's success in integrating into their corresponding projects by a margin of 4.09\% to 11.99\%, depending on the ratio of successful vs unsuccessful instances are used to train the desicion tree.
\todo{maybe add here some other answers to smaller deduced RQ's}
